\documentclass[9pt, a4paper]{article}

\usepackage{geometry}
\geometry{a4paper, margin=0.5in, top=0.5in}
\usepackage{wallpaper}
\usepackage{hyperref}
\usepackage{paracol}
\hypersetup{colorlinks=true,urlcolor=rebeccapurple}

% Do not indent paragraphs
\setlength\parindent{0in}

% \pagenumbering{gobble} does not work in this case.
% Likely due to the code for the lines needing page reference numbers.
% We use fancyhdr to modify it instead.
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % Prevent top line from appearing
% \rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}} % Format of the page numbers
\rfoot{} % Format of the page numbers

\usepackage{multicol}
% \usepackage{ragged2e}



% TYPOGRAPHY
%--------------------------------
\usepackage{fontspec} 
\usepackage{fontawesome5}
\usepackage{xunicode}
\usepackage{xltxtra}
% converts LaTeX specials (quotes, dashes etc.) to Unicode
\defaultfontfeatures{LetterSpace=-4}
%\defaultfontfeatures{Mapping=tex-text}
\setmainfont[BoldFont={Inter Semi Bold}]{Inter}
\setmonofont{JetBrains Mono}
% Cool ampersand
\newcommand{\amper}{{\fontspec[Scale=.95]{Inter}\selectfont\itshape\&}}
\usepackage{setspace}
\usepackage[inline]{enumitem}

\newcommand{\middot}{~\textperiodcentered~}

\setlist[itemize]{leftmargin=*} % removes margin from the itemize

\newlist{skills}{itemize*}{1}
\setlist[skills]{label={}, afterlabel={}, mode=unboxed,
itemjoin=\discretionary{}{}{\hbox{\middot}}}

\usepackage{lipsum,xcolor}
\newcommand\dunderline[3][-1pt]{{%
\sbox0{#3}%
\ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}

% LANGUAGE
%--------------------------------
% Set the main language for formatting purposes, just in case.
\usepackage{polyglossia}
\setmainlanguage{en-GB}


% LINES BETWEEN ITEMS
%--------------------------------
\usepackage{tikz,tikzpagenodes}
\usetikzlibrary{calc}
\usepackage{refcount}

\newcounter{mylist} % new counter for amount of lists
\newcounter{mycnt}[mylist] % create new item counter
\newcounter{mytmp}[mylist] % tmp counter needed for checking before/after current item

\newcommand{\drawoptionsconn}{black, shorten <= .5mm, shorten >= .5mm, thick}
\newcommand{\drawoptionsshort}{black, shorten <= .5mm, shorten >= -1mm, thick}

\newcommand{\myitem}{% Modified `\item` to update counter and save nodes
	\stepcounter{mycnt}%
	\item[\linkedlist{%
		i\alph{mylist}\arabic{mycnt}}]%
	\label{item-\alph{mylist}\arabic{mycnt}}%
	\ifnum\value{mycnt}>1%
	\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}<\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
		++(0,3mm) --
		(i\alph{mylist}\arabic{mycnt} |- current page text area.north);% draw short line
	\end{tikzpicture}%
	\else%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsconn] (i\alph{mylist}\arabic{mytmp}) -- (i\alph{mylist}\arabic{mycnt});% draw the connecting lines
	\end{tikzpicture}%
	\fi%
	\fi%
	\addtocounter{mytmp}{2}%
	\IfRefUndefinedExpandable{item-\alph{mylist}\arabic{mytmp}}{}{% defined
		\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}>\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
		\begin{tikzpicture}[remember picture,overlay]%
			\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
			++(0,-3mm) --
			(i\alph{mylist}\arabic{mycnt} |- current page text area.south);% draw short line
		\end{tikzpicture}%
		\fi%
	}%
	\addtocounter{mytmp}{-1}%
}

\newcommand{\linkedlist}[1]{
	\raisebox{1.5pt}[0pt][0pt]{\begin{tikzpicture}[remember picture]%
			\node (#1) [black,circle,fill,inner sep=1.5pt]{};
	\end{tikzpicture}}%
}

\newenvironment{myitemize}{%
	% Create new `myitemize` environment to keep track of the counters
	\stepcounter{mylist}% increment list counter
	\begin{itemize}
	}{\end{itemize}%
}

\newcommand{\heading}[1]{{\defaultfontfeatures{LetterSpace=0} \setmainfont{Inter} \textcolor{black} {\dunderline[-2.5pt]{1.5pt}{\small \textbf{#1}}}}}
\newcommand{\itemheading}[1]{{\defaultfontfeatures{LetterSpace=-2} \small \textbf{#1}}}
\newcommand{\subheading}[1]{{\defaultfontfeatures{LetterSpace=-2} \small \textbf{#1}}}
\newcommand{\monthyear}[1]{{\defaultfontfeatures{LetterSpace=-2} \small \textbf{#1}}}
\newcommand{\motto}[1]{{\defaultfontfeatures{LetterSpace=-3} \footnotesize #1}}

\definecolor{rebeccapurple}{rgb}{0.4,0.2,0.6}
\definecolor{sapphireblue}{rgb}{0.0,0.4,0.65}
\definecolor{slategray}{rgb}{0.44,0.5,0.56}

\begin{document}
	\begin{center}
		{\defaultfontfeatures{LetterSpace=0} \setmainfont{Inter} \textcolor{black} {\bfseries \large Vincent
Leonardo}}\\

		\motto{Aspiring AI engineer and front end developer}\smallbreak

		{\defaultfontfeatures{LetterSpace=0} \footnotesize \href{mailto:vincent@vinleonardo.com}{\textcolor{black}{\faEnvelope\ vincent@vinleonardo.com}} | \faPhone\ +65
8817 0611
		
		\href{https://www.linkedin.com/in/vincentleoooo/}{\textcolor{black}{\faLinkedin\ vincentleoooo}} | \href{https://vinleonardo.com}{\textcolor{black}{\faGlobe\ vinleonardo.com}} | \href{https://github.com/vincentleooo/}{\textcolor{black}{\faGithub\ vincentleooo}}\par}
	\end{center}
	\columnratio{0.82}
		\small
	
		\heading{ABOUT}
	\medbreak
	{A keen and passionate multidisciplinary learner obsessed with anything
technology related. Currently seeking a career in building web
interfaces and ML/DL models to make the world a better place. Particular
in crafting tools and interfaces to allow for easier usage of prediction
models and data visualisation. Enjoys collaborative work and creative
problem-solving.}
	\smallbreak
	\smallbreak
		
		\heading{EDUCATION}
	\medbreak

		\begin{paracol}{2}\itemheading{Singapore University of Technology and
Design}\\\subheading{Bachelor of Engineering with Honours (Engineering
Systems and Design)}\switchcolumn{\monthyear{Singapore}\\\monthyear{May
2019 -- Present}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Expected to graduate in September 2022.}
				\item {Awarded with the SUTD Undergraduate Merit Scholarship.}
			\end{itemize}
	\smallbreak
	
	\smallbreak
		
		\heading{EXPERIENCE}
	\medbreak
		\begin{paracol}{2}\itemheading{What Is Up,
Indonesia?}\ {\footnotesize\href{https://github.com/what-is-up-indonesia/wiui-website}{\faGithub}\ \href{https://whatisupindonesia.com}{\faGlobe}}\\\subheading{Newsletter
Writer \& Web
Developer}\switchcolumn{\monthyear{Singapore}\\\monthyear{May 2022 --
Present}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Writing weekly email newsletters discussing Indonesian news
headlines in English that reaches over 500 people.}
				\item {Writing and maintaining their website using Next.js (React)
with MDX templates.}
				\item {Exploring content management systems to implement on the
website complementing the main
\href{https://www.instagram.com/whatisupindonesia/}{Instagram\hspace{0.1em}{\tiny\faExternalLink*}}
page.}
			\end{itemize}
	\smallbreak
		\begin{paracol}{2}\itemheading{Silver Online
Service}\ {\footnotesize\href{https://github.com/vincentleooo/silver-online-service-website}{\faGithub}\ }\\\subheading{Marketing
Coordinator \& Web
Developer}\switchcolumn{\monthyear{Singapore}\\\monthyear{May 2022 --
Present}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Developing a website (in-progress) to increase reach towards
children of elderly parents who are struggling with smartphone usage.}
				\item {Advising for the creation of the startup company's brand
identity and design for Instagram posts and the website.}
			\end{itemize}
	\smallbreak
		\begin{paracol}{2}\itemheading{Shopee Pte
Ltd}\ {\footnotesize\ }\\\subheading{Regional Operations (Fraud)
Intern}\switchcolumn{\monthyear{Singapore}\\\monthyear{May 2021 -- Sep
2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Wrangled and examined large user behavioural datasets using
the Apache Hive ecosystem, Python, and SQL.}
				\item {Ideated rules that reduce instances of fraud, tested and
analysed impact thereof with three other departments.}
			\end{itemize}
	\smallbreak
	
	\smallbreak
		
		\heading{PROJECTS \& COMPETITIONS}
	\medbreak
		\begin{paracol}{2}\itemheading{Gait Recognition Model and
Analytics} {\footnotesize }\\\subheading{Klass Engineering Pte
Ltd}\switchcolumn{\monthyear{Singapore}\\\monthyear{Jan 2022 --
Present}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Leading a team of five from two different pillars to model
unique identification of people based on their gait alone.}
				\item {Synthesising a full-stack pipeline from video feed to
classification using React, FastAPI, OpenCV, and OpenGait models.}
			\end{itemize}
	\smallbreak
		\begin{paracol}{2}\itemheading{Music Genre
Classification} {\footnotesize\href{https://github.com/nugglet/Music-Genre-Classification}{\faGithub} }\\\subheading{SUTD
50.039 Theory and Application of Deep
Learning}\switchcolumn{\monthyear{Singapore}\\\monthyear{Jan 2022 -- May
2022}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Crafted a lightweight parallel CNN model to classify music
genres using the GTZAN dataset to achieve around 80\% accuracy.}
				\item {Split inputs into three-second chunks, and ensembling
predictions based on these chunks for unseen data of any length.}
				\item {Created a simple CLI application and a
\href{https://github.com/vincentleooo/react-fastapi}{prototype web interface\hspace{0.1em}{\tiny\faExternalLink*}}
for ease-of-use.}
			\end{itemize}
	\smallbreak
		\begin{paracol}{2}\itemheading{Agent-Based Modelling for Airport
Arrivals in a Post-Pandemic
World} {\footnotesize\href{https://github.com/vincentleooo/sma-airport-model}{\faGithub} \href{https://github.vinleonardo.com/sma-airport-model/}{\faGlobe}}\\\subheading{SUTD
40.015 Simulations Modelling
Analysis}\switchcolumn{\monthyear{Singapore}\\\monthyear{Oct 2021 -- Dec
2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Project was highlighted for the course in the
\href{https://esd.sutd.edu.sg/files/ESD-Spring-Newsletter-2022.pdf}{ESD pillar newsletter\hspace{0.1em}{\tiny\faExternalLink*}}
in early 2022.}
				\item {Managed the team of three in designing the architecture and
user experience of the simulation using d3.js.}
			\end{itemize}
	\smallbreak
		\begin{paracol}{2}\itemheading{Synthesis Sustainability IRL Data
Challenge} {\footnotesize\href{https://github.com/vincentleooo/synthesis-sustainability-2021}{\faGithub} \href{https://vinleonardo.com/synthesis-sustainable-competition-2021/}{\faGlobe}}\\\subheading{Synthesis
\& Treatsure}\switchcolumn{\monthyear{Singapore}\\\monthyear{Oct 2021 --
Nov 2021}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Directed the team of three to win
\href{https://www.linkedin.com/feed/update/urn:li:activity:6872448218022727680/}{third place\hspace{0.1em}{\tiny\faExternalLink*}}
in the data science challenge among around 135 participants.}
				\item {Modelled word associations and sentiments on food surplus
consumption from Twitter and Instagram posts in the past five years to
consult Treatsure on persuading more people to consume surplus food.}
			\end{itemize}
	\smallbreak
	
	\smallbreak
	
		\heading{CO-CURRICULAR ACTIVITIES}
	\medbreak
		\begin{paracol}{2}\itemheading{60.002 AI Applications in
Design} {\footnotesize }\\\subheading{Teaching
Assistant}\switchcolumn{\monthyear{Singapore}\\\monthyear{Jan 2022 --
May 2022}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Mentored groups in their projects involving web scraping and
text analysis using various Python packages.}
				\item {Taught Python and TensorFlow installation, usage, and
debugging skills.}
			\end{itemize}
	\smallbreak
		\begin{paracol}{2}\itemheading{SUTD 9th Student
Government} {\footnotesize }\\\subheading{Advisor, Media \&
Marketing}\switchcolumn{\monthyear{Singapore}\\\monthyear{Nov 2020 --
Feb 2022}}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Advised and assisted the Media \& Marketing team of seven on
student engagement projects in the university.}
				\item {Co-led the Mental Health Awareness Week initiative, reaching
over 1000 people through videos and Telegram Stickers.}
			\end{itemize}
	\smallbreak
		
	\smallbreak

		\smallbreak
		\heading{ADDITIONAL INFORMATION}
	\medbreak
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Native English and Bahasa Indonesia speaker.}
				\item {Comfortable in Linux/Unix-based systems and shell scripting,
especially in web servers and for deep learning purposes.}
				\item {Enjoys history, linguistics, music, and tinkering with
technology to automate various things, including
\href{https://github.com/vincentleooo/resume}{this résumé\hspace{0.1em}{\tiny\faExternalLink*}}.}
			\end{itemize}
	\end{document}